Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-09 paper/paper.qmd
Added more past works to intro and add data evalulation to survey (not done)

In this paper, to see what factors could impact the likelihood of a homicide case going unsolved, we analyzed data provided by The Washington Post [@datahomicides] that were compiled by their reporters on homicide cases and their status from 2010 to 2017. Previously, The Washington Post has used the data they compiled to construct a map and pinpointing places unsolved homicides occur [@citewashingtonpostmap]. However, specific analysis looking at the differences in case characteristics between specific two US cities like Chicago and Los Angeles has not been done previously. In our findings, it indicates that a majority of unsolved homicide victims from 2010 to 2017 are Black or Hispanic and they are likely to be male but their age does not impact if there case goes unsolved or not. We also found that unsolved homicides are more likely to occur in Chicago compared to Los Angeles from 2010 to 2017. From our analysis, most unsolved homicide cases occurred during the middle and later half of the year with there being a jump in unsolved cases from 2016 onwards. These findings could inform the public and police departments about populations more vulnerable to homicide cases going unsolved and cities to be more alert about such as Chicago with homicide clearance rates.

@@

>>>>

In this paper, to see what factors could impact the likelihood of a homicide case going unsolved, we analyzed data provided by The Washington Post [@datahomicides] that were compiled by their reporters on homicide cases and their status from 2010 to 2017. Previously, The Washington Post has used the data they compiled to construct a map and pinpointing places unsolved homicides occur [@citewashingtonpostmap]. In another study, @citeIndiana looked at factors that contributed to the low homicide clearance rates in Indianapolis, Indiana across different neighbourhoods. They found that there was an association between neighbourhoods with higher arrest rates and them having a higher chance of homicide clearance [@citeIndiana]. However, specific analysis looking at the differences in case characteristics between specific two US cities like Chicago and Los Angeles has not been done previously. In our findings, it indicates that a majority of unsolved homicide victims from 2010 to 2017 are Black or Hispanic and they are likely to be male but their age does not impact if there case goes unsolved or not. We also found that unsolved homicides are more likely to occur in Chicago compared to Los Angeles from 2010 to 2017. From our analysis, most unsolved homicide cases occurred during the middle and later half of the year with there being a jump in unsolved cases from 2016 onwards. These findings could inform the public and police departments about populations more vulnerable to homicide cases going unsolved and cities to be more alert about such as Chicago with homicide clearance rates.

@@

## Overview and Evaluation of The Washington Post’s Dataset {#sec-data-evalulation}
- TODO: Make sure to link evaluation to literature

### Overview

### Sampling Approach
- what is the population, frame, and sample;
- how is the sample recruited;
- what sampling approach is taken, and what are some of the trade-offs of this; 
- how is non-response handled;

### Strengths and limitations
- what is good and bad about the sampling.
